Deeply Virtual Compton Scattering measurement off bound protons

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex

%asymmetries
Experimentally, $A_{LU}$ is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
negative beam-helicity states, and $P_{B}$ is the longitudinal beam 
polarization.

@@

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure}

@@

\begin{figure}[tb]
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
   measurements for the incoherent (coherent) enriched region 
   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
   from \cite{simonetta_2}.  } \label{fig:alu90}
\end{figure}

>>>>

%asymmetries
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

Experimentally, $A_{LU}$ is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
negative beam-helicity states, and $P_{B}$ is the longitudinal beam 
polarization.

@@

@@

\begin{figure}[tb]
\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
   represent the statistical uncertainties, while the gray bands represent the 
   systematic uncertainties. On the middle plot the curves are theoretical 
   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
   measurements for the incoherent (coherent) enriched region 
   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
   from \cite{simonetta_2}.  } \label{fig:alu90}
\end{figure}
